---
name: Holly A. Zaharchuk
position: "PhD Candidate (she/her)"
address: "University Park, Pennsylvania, United States"
email: "hzaharchuk@psu.edu"
www: www.hzaharchuk.com
orcid: "0000-0002-7693-7807"
github: hollzzar
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: TRUE
docname: "Curriculum vitae"
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```

# Research interests

My research interests lie at the intersection of cognitive psychology and sociolinguistics. I use neuropsychological (EEG) and behavioral methods to understand how linguistic, cognitive, and social factors interact during language processing. My particular areas of study include phonetic and syntactic variation, bilingual code-switching, and network models of language.

# Education

```{r education}
#Read in data
education <- read_csv("./data/education.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
education <- education %>%
  arrange(desc(begin), end) %>%
  group_by(degree) %>%
  mutate(where = ifelse(n() > 1,
                         as.character(glue("{nth(city, 1)}, {nth(region, 1)}, {nth(country,1)} 
                                           and {nth(city, 2)}, {nth(region, 2)}, {nth(country,2)}")),
                         as.character(glue("{city}, {region}")))) %>% 
  ungroup() %>%
  mutate(when = ifelse(is.na(end),
                       as.character(glue("{year(begin)} - present")),
                       as.character(glue("{year(begin)} - {year(end)}"))))

#Print education information
education %>% 
  detailed_entries(degree, when, university, where, c(advisor, thesis), .protect = FALSE)
```

# Honors and awards

```{r honors}
#Read in data
honors <- read_csv("./data/honors.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
honors <- honors %>%
  arrange(order) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(begin), "Postponed due to COVID-19",
                       ifelse(is.na(year(end)),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                              ifelse(end==begin,
                                     as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                                     as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}"))))))

#Print honors and awards information
honors %>% 
  detailed_entries(when=when, with=award, where=university, what=desc)
```

# Publications

```{r scholarship}
#Print bibliography
bibliography_entries("my-cv.bib")
```
# Presentations

```{r presentations}
#Print bibliography
bibliography_entries("my-presentations.bib")
```

# Invited talks

- Processing Variation (ProVAR) group led by Dr. Marije Soto, Federal University of Rio de Janeiro
- Psycholinguistic fieldwork guest lecture for Dr. Colleen Balukas, University at Buffalo (SUNY) 

# Research experience

```{r experience-research}
#Read in data
experience <- read_csv("./data/experience.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
experience <- experience %>%
  arrange(!is.na(desc(end)), desc(end), begin) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print research experience information
experience %>% 
  dplyr::filter(!is.na(pi)) %>%
  detailed_entries(position, when, organization, where, c(pi, desc_1, desc_2), .protect = FALSE)
```

# Professional experience

```{r experience-prof}
#Print professional experience information
experience %>% 
  dplyr::filter(is.na(pi)) %>%
  detailed_entries(position, when, organization, where, c(pi, desc_1, desc_2), .protect = FALSE)
```

# Teaching experience

```{r teaching}
#Read in data
teaching <- read_csv("./data/teaching.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
teaching <- teaching %>%
  arrange(desc(begin), end) %>%
  group_by(course) %>%
  mutate(where = ifelse(n() > 1,
                         as.character(glue("{nth(city, 1)}, {nth(region, 1)}, {nth(country,1)} 
                                           and {nth(city, 2)}, {nth(region, 2)}, {nth(country,2)}")),
                         as.character(glue("{city}, {region}")))) %>% 
  ungroup() %>%
  mutate(when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print teaching information
teaching %>% 
  detailed_entries(role, when, course, university, c(instructor, desc_1, desc_2), .protect = FALSE)
```

# Outreach

```{r outreach}
#Read in data
outreach <- read_csv("./data/outreach.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
outreach <- outreach %>%
  arrange(!is.na(desc(end)), desc(end), begin) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print outreach information
outreach %>% 
  detailed_entries(position, when, organization, where, c(desc_1, desc_2), .protect = FALSE)
```

# Community service

```{r service}
# Community service
# echo=FALSE, eval=FALSE

#Read in data
service <- read_csv("./data/service.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
service <- service %>%
  arrange(!is.na(desc(end)), desc(end), begin) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print service information
service %>% 
  detailed_entries(position, when, organization, where, c(desc_1, desc_2))
```

# Academic service

- Ad hoc reviewing
  - *Brain and Language*
  - *Journal of Experimental Psychology: Learning, Memory, and Cognition*
  - *Scientific Reports*
- Workshops and tutorials
  - Leader: [R Markdown for Graduate Students](https://github.com/hollzzar/markdown-tutorial) (2020), [Creating HTML Reports with R Markdown](https://github.com/hollzzar/reports-with-markdown) (2020)
  - Assistant: [R Bootcamp](https://github.com/psu-psychology/r-bootcamp-2019) (2019) led by Dr. Rick Gilmore
- [R Markdown for Psychology Graduate Students](https://www.hzaharchuk.com/rmarkdown-guide/) resource

# Skills

- Natural languages: English, Spanish (B2/Intermediate)
- Programming languages: R, MATLAB, SQL, Python
- Software: E-Prime, Praat, Microsoft Suite, Adobe Suite
- Typesetting: R Markdown, \LaTeX

# Affiliations

- Center for Language Science
- Cognitive Neuroscience Society
- Psychonomic Society
- Society for the Neurobiology of Language
- Women in Cognitive Science
