---
name: Holly A. Zaharchuk
position: "Postdoctoral researcher (she/her)"
address: "Storrs, Connecticut, United States"
email: "holly.zaharchuk@uconn.edu"
www: www.hzaharchuk.com
orcid: "0000-0002-7693-7807"
github: hollzzar
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: TRUE
docname: "Curriculum vitae"
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```

# Research interests

How does the brain respond to linguistic variation? I use a combination of neural (EEG, fMRI, TMS) and behavioral (eye-tracking, manual response) methods to study the perception, representation, and processing of diverse speech signals. I am particularly interested in the effects of multilingual and multilectal experience on the language system.

# Education

```{r education}
#Read in data
education <- read_csv("./data/education.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
education <- education %>%
  arrange(desc(begin), end) %>%
  group_by(degree) %>%
  mutate(where = ifelse(n() > 1,
                         as.character(glue("{nth(city, 1)}, {nth(region, 1)}, {nth(country,1)} 
                                           and {nth(city, 2)}, {nth(region, 2)}, {nth(country,2)}")),
                         as.character(glue("{city}, {region}")))) %>% 
  ungroup() %>%
  mutate(when = ifelse(is.na(end),
                       as.character(glue("{year(begin)} - present")),
                       as.character(glue("{year(begin)} - {year(end)}"))))

#Print education information
education %>% 
  detailed_entries(degree, when, university, where, c(advisor, thesis), .protect = FALSE)
```

# Honors and awards

```{r honors}
#Read in data
honors <- read_csv("./data/honors.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
honors <- honors %>%
  arrange(order) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(begin), "Postponed due to COVID-19",
                       ifelse(is.na(year(end)),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                              ifelse(end==begin,
                                     as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                                     as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}"))))))

#Print honors and awards information
honors %>% 
  detailed_entries(when=when, with=award, where=university, what=desc)
```

# Publications

```{r scholarship}
#Print bibliography
bibliography_entries("my-cv.bib")
```

# Works in progress

```{r wips}
#Print bibliography
bibliography_entries("my-wips.bib")
```

# Presentations

```{r presentations}
#Print bibliography
bibliography_entries("my-presentations.bib")
```

# Invited talks

```{r invited}
#Print bibliography
bibliography_entries("my-invites.bib")
```

# Employment history

```{r experience-research}
#Read in data
experience <- read_csv("./data/experience.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
experience <- experience %>%
  arrange(!is.na(desc(end)), desc(end), begin) %>%
  mutate(where = as.character(glue("{city}, {region}")),
         when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print research experience information
experience %>% 
  detailed_entries(position, when, organization, where, 
                   c(pi, desc_1, desc_2), .protect = FALSE)
```

# Teaching experience

```{r teaching}
#Read in data
teaching <- read_csv("./data/teaching.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")))

#Create where and when fields
teaching <- teaching %>%
  arrange(desc(begin), end) %>%
  group_by(course) %>%
  mutate(where = ifelse(n() > 1,
                         as.character(glue("{nth(city, 1)}, {nth(region, 1)}, {nth(country,1)} 
                                           and {nth(city, 2)}, {nth(region, 2)}, {nth(country,2)}")),
                         as.character(glue("{city}, {region}")))) %>% 
  ungroup() %>%
  mutate(when = ifelse(is.na(year(end)),
                       as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - present")),
                       ifelse(end==begin,
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)}")),
                              as.character(glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - {month(end, label = TRUE, abbr = TRUE)} {year(end)}")))))

#Print teaching information
teaching %>% 
  detailed_entries(role, when, course, university, c(instructor, desc_1, desc_2), .protect = FALSE)
```

# Academic service

- Mentor for the \href{https://magic.initiative.uconn.edu/}{\underline{Mentoring Aspiring Graduate students and building an Inclusive Community}} program
- Ad hoc reviewing
  - *Brain and Language*
  - *Cognitive, Affective, and Behavioral Neuroscience*
  - *Journal of Experimental Psychology: Learning, Memory, and Cognition*
  - *Scientific Reports*
- Workshops and tutorials
  - Leader: \href{https://github.com/hollzzar/markdown-tutorial}{\underline{R Markdown for Graduate Students}} (2020) for 20 students, \href{https://github.com/hollzzar/reports-with-markdown}{\underline{Creating HTML Reports with R Markdown}} (2020) for 10 students
  - Assistant: \href{https://github.com/psu-psychology/r-bootcamp-2019}{\underline{R Bootcamp}} led by Dr. Rick Gilmore for 50+ students
- \href{https://www.hzaharchuk.com/rmarkdown-guide/}{\underline{R Markdown for Psychology Graduate Students}} resource

# Skills

- Natural languages: English, Spanish (B2/Intermediate)
- Programming languages: R, MATLAB, Python, SQL
- Software: E-Prime, Praat, Microsoft Suite, Adobe Suite
- Typesetting: R Markdown, \LaTeX

# Affiliations

- Center for Language Science
- Cognitive Neuroscience Society
- Psychonomic Society
- Society for the Neurobiology of Language
- Women in Cognitive Science
